The United States government defines {\it critical infrastructure} as ``systems
and assets, whether physical or virtual, so vital to the United States that the
incapacity or destruction of such systems and assets would have a debilitation
impact on security, national economic security, national public health or
safety, or any combination of those matters''~\cite{patriotact}. Internet
connectivity, a fundamental requirement for modern communication, is
undoubtedly such a system. 
Businesses~\cite{something?} and governments~\cite{cyberspacepolicy} hence 
value the physical security of Internet infrastructure 
to disaster or attack.


In this paper, we provide a brief glance at physical Internet resilience by focusing on
a model of geographic locations where multiple
networks converge to interconnect. Damage to an Internet Exchange Point (IXP) or Point-of-Presence (PoP) are worst-case scenarios for physical disaster, as these locations provide connectivity between anywhere from two to hundreds of networks.
 Building on prior work which develops techniques for identifying
formal IXPs~\cite{ixps-mapped}, discovering PoPs in general~\cite{iplane}, and pinpointing border
routers~\cite{asbrsomething}, we develop an AS connectivity graph that focuses
on the locations where peering takes place.  We then consider the behavior of
an adversary who seeks to maximize damage to this connectivity graph.  Such an
adversary might wish to disconnect two Tier 1 networks, isolate a large number
of networks, or partition a geographic region from the rest of the Internet.
We consider each in turn.


We are not the first to evaluate Internet resilience to
failures~\cite{michigan, measuringresilience, resilience-under-bgp, resilience-complex-networks}.  
Our contribution is to consider physical locations of conncetivity
 as {\it failure points}.
Previous work focused on the impact of severing logical
links, that is, declaring that two networks had been entirely disconnected.
This overestimates realistic damage in some cases, and underestimates in
others.  For example, it is highly unlikely that two Tier 1 networks would be
partitioned in any single event.  These networks have global footprints and
connect at multiple physical locations.  Thus, disconnecting Tier 1 networks is
an overestimate of damage in all scenarios except a coordinated attack.  On the
other hand, disconnecting logical links one by one ignores the physical reality
that any disaster that strikes a link in shared infrastructure such as an IXP
is likely to impact a large number of links.  In this case, modeling failure of
a single logical link is an underestimate.  We argue that focusing on physical
connectivity points is a more realistic model of the impact of physical disaster. 

\eat{ Not true!
 
Second, we consider resilience in an adversarial setting.  Recent events in
Egypt~\cite{thenews} and other countries involved government intervention to
sever Internet access in order to limit communication between revolutionaries
and the outside world.  Further, the criticality of Internet communication
makes it a prime target for terrorist attack.  Attacks by any human entity may
involve damage to one or more physical locations.  Hence, our analysis is a
superset of previous work which focused primarily on natural disaster or
sideffects from events in a single location.
}

Before we move forward, we clarify the scope of our goals.  
Evaluations of AS-level connectivity graphs show that traceroute-based
topologies like those that we rely upon are in many ways
incomplete~\cite{walter}.  For instance, policy compliant routing ensures that
measurements made with only limited vantage points cannot observe peering
relationships between networks where neither network contains a measurement
vantage point.  Further, `backup links', which are provisioned for the case of
failure but otherwise unused, cannot be observed since no traffic flows across
these links when the primary links are available.  These and other impediments
mean that any analysis over measurement-based graphs may be missing critical
information.  Thus, the results of our study should not be considered hard and
fast projections of Internet connectivity.  Instead, we aim only to provide
{\it estimates} and {\it bounds} on the impact of attack on Internet
infrastructure.

Our results estimate that \ldots
\justine{My hypotheses: (1) we find that Tier-1's are too well connected to feasibly partition - we can echo the argument from that paper Kristin found that the threat is misconfiguration or attacks on the control plane, but certainly not the physical infrastructure. (2) The exact opposite is true for small networks - that taking out a single IXP in many cases is enough to knock offline dozens of ASes and hundreds or thousands of prefixes. WRT geographic regions, I am less sure - hopefully we can identify the Egypts of the world?}

The remainder of the paper is organized as follows.
Section~\ref{sec:connectivity} discusses our dataset and model of the physical
connectivity of Internet infrastructure.  Section~\ref{sec:algos} provides the
algorithms we used in analyzing this model.  Section~\ref{sec:results}
describes our discoveries from applying these algorithms.  Finally, we discuss
related work in \S~\ref{sec:relatedwork} and conclude in
\S~\ref{sec:conclusion}.

