\documentclass{sig-alternate-10pt}
%\documentclass[letterpaper,11pt]{article}
\usepackage{url}
%\usepackage{usenix,epsfig,endnotes}
%\usepackage{fullpage} 
%\setlength{\textheight}{9in}
%\setlength{\textwidth}{6.75in}
%\setlength{\oddsidemargin}{-.125in}
\usepackage{graphicx}
%\usepackage{subfigure}
%\usepackage{ifpdf}
%\usepackage{multicol}
%\usepackage{amsmath, amssymb, amsthm}
%\usepackage{rotating}
\usepackage{multirow}
\usepackage{rotating}
%\onehalfspacing

%COMMENT FOR FINAL VERSION
\newcommand{\tbd}[1]{[{\bf{#1}}]}
\newcommand{\justine}[1]{[{\bf justine: {#1}}]}
\newcommand{\shaddi}[1]{[{\bf shaddi: {#1}}]}
\newcommand{\kristin}[1]{[{\bf kristin: {#1}}]}

%UNCOMMENT FOR FINAL VERSION
%\newcommand{\tbd}[1]{}
%\newcommand{\justine}[1]{}
%\newcommand{\shaddi}[1]{}
%\newcommand{\kristin}[1]{}


\newcommand{\ie}{{\it i.e.}}
\newcommand{\eg}{{\it e.g.}}
\newcommand{\eat}[1]{}

%\newcommand{\tbd}[1]{}
%\setlength\topmargin{0in}
%\usepackage{verbatim}
%\usepackage[compact]{titlesec}
%\usepackage[small]{caption}
\usepackage{times}
%\titlespacing{\section}{0pt}{*0}{*0}
%\titlespacing{\subsection}{0pt}{*0}{*0}
%\titlespacing{\subsubsection}{0pt}{*0}{*0}
%\titlespacing{\abstract}{0pt}{*0}{*0}
%%REPLACES ITEMIZE

\title{Modeling Regional Failures in Interdomain Connectivity}
\author{\begin{tabular}{ccc} Shaddi Hasan & Justine Sherry & Kristin Stephens\\
%        \begin{multicols}{2}{{\it Draft - Please do not distribute.}}\\
        \end{tabular}\\
    University of California, Berkeley\titlenote{Authors listed
    alphabetically.}\\\\
        \large
        {\it CS270 Final Project}}
        \normalsize
%\author{Paper \#69, 14 Pages}
\date{}
\begin{document}    
    \maketitle

        %Internet interdomain resilience requires engineering for failure, from
        %deploying robust routing protocols, to establishing logical
        %connectivity redundancy (multihoming), to building redundant
        %interomain physical links.  
    \abstract{\it
        Earthquakes, hurricanes, and other regional disasters can 
        stress Internet interdomain connectivity.  Because of their widespread
        impact, these disasters can cause failures of entire exchange points or
        severance of long distance cables, leading to correlated failures in
        interdomain connectivity.  In this paper we develop a model, geodesic
        failure regionalization, to explore the impact of regional failures on
        AS connectivity.  We map logical AS connectivity links to geographic
        regions where peering occurs to model the regional redundancy of
        peering connections.
        By modeling the redundancy of logical AS
        connectivity, we can perform
        finer-grained analysis of the impact of catastrophe than work which
        relies only on logical AS connectivity alone.  
        Our data demonstrates that most transit-providing networks peer in redundant locations, such that small physical disasters ar unlikely to partition two peering networks.    
    However, our data also includes geographic regions served by only a limited number of ASes with limited peering to external networks, leaving these geographic regions suceptible to disconnection after damage to only a few regions containing all of their egress connectivity.
    }
    
    \section{Introduction}
        \input{introduction}

    \section{Connectivity Model}
        \label{sec:connectivity_model}
        \input{connectivity_model}

    \section{Measuring Connectivity}
        \label{sec:quant_connect}
        \input{quant_connect}

    \section{Regional Failure Analysis}
        \label{sec:failures} 
        \input{failure_analysis}
        
    \section{Related Work}
        \label{sec:related_work}
        \input{related_work}

    \section{Conclusion}
        \label{sec:conclusion}    
        \input{conclusion}


%\scriptsize
%\small
\bibliographystyle{abbrv}
\bibliography{cite}

%\input{appendix}

\end{document}
